### 2023-08-22 manuscript.tex
initial commit

\documentclass{optica-article}

\journal{opticajournal} % for journals or Optica Open

\articletype{Research Article}

\usepackage{lineno}
\linenumbers % Turn off line numbering for Optica Open preprint submissions.

\begin{document}

\title{Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD}

\author{Author One,\authormark{1} Author Two,\authormark{2,*} and Author Three\authormark{2,3}}

\address{\authormark{1}Peer Review, Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
\authormark{2}Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
\authormark{3}Currently with the Department of Electronic Journals, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA}

\email{\authormark{*}opex@optica.org} %% email address is required; see note below about the corresponding author designation

% use {asbstract*} to suppress the copyright line. Copyright information will be added in production

\begin{abstract*} 
Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors. If leveraged to it's full potential, PNR capabilty can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing. Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors. In this work we put a differential readout SNSPD to the ultimate test. We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock. We show the detector is capable of discriminating the arrival time of photons to 50\textasciitilde ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses. We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
\end{abstract*}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

This is the introduction with some latex \(\frac{33}{44}\)

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

This is the methods section with some latex \(\frac{33}{44}\)

Here is citation \cite{Dolinar2011Photon} and here is the rest of the sentence.

\bibliography{references}

\end{document}

### 2023-08-22 manuscript.tex
Update on Overleaf.
testing
overleaf update

@@
 
+Something unique.
+
+\hypertarget{fig:channel_data}{%
+\begin{figure}
+\centering
+\includegraphics[width=1\textwidth,height=\textheight]{chapter_03/figs_03/8ch_bar_graph_high_power_light.pdf}
+\caption[{Fidelity and rates across 8 channel pairs.}]{\textbf{Fidelity and rates across 8 channel pairs} a) Fidelity for the main 8 channel pairs, measured at a high (5.17 Amps) and a low ( 1.2 Amps) SHG pump power setting.
+Each power setting results in similar \(\mu\) for all channels: \(\mu_{low}\) = 5.6e-5 \(\pm\) 9e-6 and \(\mu_{high}\) = 6.1e-3 \(\pm\) 3e-4.
+b) Rate metrics for the 8 channel pairs at the same high and low power settings.
+The range of possible values for distillable entanglement rate is spanned by the yellow regions, bounded above by log-negativity and below by coherent information.
+Rates shown assume readout of all 4 available interferometer ports, based on data measured using one port each at Alice and Bob}
+\label{fig:channel_data}
+\end{figure}
+}
+
 \hypertarget{methods}{%

### 2023-08-22 manuscript.tex
overleaf update
Update on Overleaf.

@@
 \begin{abstract*}
+
+\end{abstract*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Abstract}
+
 Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors.
@@
 We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
-\end{abstract*}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
-\hypertarget{introduction}{%
-\subsection{Introduction}\label{introduction}}
+\subsection{Introduction}
 
@@
 \centering
-\includegraphics[width=1\textwidth,height=\textheight]{chapter_03/figs_03/8ch_bar_graph_high_power_light.pdf}
+\includegraphics[width=1\textwidth]{./figs_03/8ch_bar_graph_high_power_light.pdf}
 \caption[{Fidelity and rates across 8 channel pairs.}]{\textbf{Fidelity and rates across 8 channel pairs} a) Fidelity for the main 8 channel pairs, measured at a high (5.17 Amps) and a low ( 1.2 Amps) SHG pump power setting.
@@
 
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
+this is where I add a citation
+
+\subsection{Methods}
 

### 2023-08-22 manuscript.tex
overleaf update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Abstract}
+\section{Abstract}
 
@@
 We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock.
-We show the detector is capable of discriminating the arrival time of photons to 50\textasciitilde ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
+We show the detector is capable of discriminating the arrival time of photons to 50.\ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
 We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
 
-\subsection{Introduction}
+\section{Introduction}
 
@@
 
-\subsection{Methods}
+\section{Methods}
 

### 2023-08-22 manuscript.tex
overleaf update

@@
 We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock.
-We show the detector is capable of discriminating the arrival time of photons to 50.\ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
+We show the detector is capable of discriminating the arrival time of photons to 50.~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
 We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.

### 2023-08-22 manuscript.tex
overleaf update

@@
 We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock.
-We show the detector is capable of discriminating the arrival time of photons to 50.~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
+We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
 We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.

### 2023-08-22 manuscript.tex
overleaf update

@@
 
-This is the introduction with some latex \(\frac{33}{44}\)
+This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
+The investigation was driven by recent advancements in NbN SNSPDs, which have achieved a jitter as low as 50 ps at the FW(1/100)M level, enabling the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
+The aim was to increase the data rate by a factor of 10, from 2 GHz to 20 GHz, in the next generation of the Deep Space Optical Communication (DSOC) project.
 
-Something unique.
+During the course of this study, the focus shifted towards investigating the impact of photon number resolution (PNR) on the low jitter detection of optical pulses.
+PNR can have an unintended impact on the demonstration of high-rate PPM, and therefore a thorough study of its effects was deemed crucial.
+A novel PNR cancellation technique was developed and applied to successfully demonstrate high-rate PPM.
+This technique is considered essential for future low-jitter applications of SNSPDs that exhibit photon-number effects.
 
-\hypertarget{fig:channel_data}{%
-\begin{figure}
-\centering
-\includegraphics[width=1\textwidth]{./figs_03/8ch_bar_graph_high_power_light.pdf}
-\caption[{Fidelity and rates across 8 channel pairs.}]{\textbf{Fidelity and rates across 8 channel pairs} a) Fidelity for the main 8 channel pairs, measured at a high (5.17 Amps) and a low ( 1.2 Amps) SHG pump power setting.
-Each power setting results in similar \(\mu\) for all channels: \(\mu_{low}\) = 5.6e-5 \(\pm\) 9e-6 and \(\mu_{high}\) = 6.1e-3 \(\pm\) 3e-4.
-b) Rate metrics for the 8 channel pairs at the same high and low power settings.
-The range of possible values for distillable entanglement rate is spanned by the yellow regions, bounded above by log-negativity and below by coherent information.
-Rates shown assume readout of all 4 available interferometer ports, based on data measured using one port each at Alice and Bob}
-\label{fig:channel_data}
-\end{figure}
-}
+This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
+The investigation was driven by recent advancements in NbN SNSPDs, which have achieved a jitter as low as 50 ps at the FW(1/100)M level, enabling the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
+The aim was to increase the data rate by a factor of 10, from 2 GHz to 20 GHz, in the next generation of the Deep Space Optical Communication (DSOC) project.
 
-this is where I add a citation
+During the course of this study, the focus shifted towards investigating the impact of photon number resolution (PNR) on the low jitter detection of optical pulses.
+PNR can have an unintended impact on the demonstration of high-rate PPM, and therefore a thorough study of its effects was deemed crucial.
+A novel PNR cancellation technique was developed and applied to successfully demonstrate high-rate PPM.
+This technique is considered essential for future low-jitter applications of SNSPDs that exhibit photon-number effects.
+
+\subsection{Pulse Position Modulation for Deep Space Communication}
+
+Deep Space Optical Communication has been a growing field of study in recent years, as researchers look for ways to communicate with spacecraft that are far away from Earth.
+In this article, we will focus on the use of Pulse Position Modulation (PPM) for deep space optical communication.
+
+While other modulation techniques such as quadrature amplitude modulation (QAM) have been used in the past, it has been shown that in the photon-starved regime, PPM is the best approach for sending data.
+This is because there is not enough light to measure the phase of the signal.
+
+PPM relies on sending one optical pulse carrying M bits of information in one of \(2^M\) possible time slots.
+For M = 2, this corresponds to sending an early pulse to represent a 0 bit and a late pulse to represent a 1 bit.
+
+The main challenge in deep space optical communication is the high loss and distance that the link must traverse.
+This limits the communication from the spacecraft, as it is limited by the power available on the spacecraft.
+This means that the communication protocol is limited by the number of bits that can be sent per unit of energy on the spacecraft, also known as photon information efficiency or bits per photon.
+
+For large M, PPM achieves high photon information efficiency, allowing for the saving of power on the spacecraft and the sending of more information with fewer photons.
+The existing deep space optical communication project uses M up to \(2^8 = 256\), meaning that 8 bits of data are carried in each optical pulse.
+
+In this project, we aimed to demonstrate even higher photon information efficiency by using M values up to 2048, or 11 bits of data per optical pulse.
+
+While the use of large M values increases photon information efficiency, it also decreases the data rate of the system.
+This is because the number of time bins needed per optical pulse scales exponentially with the amount of data in each pulse.
+Therefore, for a given fixed clock rate and time bin duration, the data rate decreases dramatically for higher M values.
+
+Using M values much larger than 11 is unlikely to be practical in future deep space optical communication systems.
+However, the data rate of these systems can be increased linearly by increasing the clock rate or bin size of the experiment.
+This is possible with the use of low jitter detection systems or low jitter superconducting nanowire single-photon detectors (SNSPDs).
+
+\subsection{Development of a modulation source}
+
+The communication signal on a spacecraft is generated by utilizing a Continuous Wave (CW) seed laser that is carved by a fast intensity modulator.
+The resulting low-power pulsed signal is then amplified by an Erbium Doped Fiber Amplifier (EDFA) to increase its transmission power to Earth.
+The majority of the power used by the spacecraft for communication scales with the number of optical pulses due to the EDFA.
+
+In our experiment, the 20 GHz repetition rate was limited by the jitter of the Single-Photon Detectors (SNSPDs) that we intended to use.
+These detectors have a Full Width at Half Maximum (FW(1/100)M) jitter of approximately 50 ps.
+To ensure that the response function of the entire experiment had jitter of around 50 ps FW(1/100)M, we needed to build a Pulsed Phase Modulation (PPM) source with ultra-short optical pulses.
+
+Carving a CW laser with our system would have introduced excessive timing uncertainty due to the limited ability of even the fastest lithium niobate intensity modulators to carve pulses with widths below 20 ps.
+The added jitter from modulated CW pulses, combined with the jitter of the detectors, would have exceeded the 20 GHz/50 ps slot width requirement.
+
+Therefore, we chose to carve pulses from a mode-locked laser.
+This approach allows for extremely short pulses in time, with the modulators responsible for sufficiently reducing any surrounding unwanted pulses.
+The temporal width of the modulator pulse response must be extremely short and able to modulate from `off' to `on' within a time frame of the order of the 50 ps bin width.
 

### 2023-08-22 manuscript.tex
overleaf update

@@
 \begin{abstract*} 
-
-\end{abstract*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Abstract}
-
 Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors.
@@
 In this work we put a differential readout SNSPD to the ultimate test.
-We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock.
+We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
 We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
 We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
+\end{abstract*}
 
-\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
-\subsection{Pulse Position Modulation for Deep Space Communication}
+\hypertarget{pulse-position-modulation-for-deep-space-communication}{%
+\subsection{Pulse Position Modulation for Deep Space Communication}\label{pulse-position-modulation-for-deep-space-communication}}
 
@@
 
-\subsection{Development of a modulation source}
+\hypertarget{development-of-a-modulation-source}{%
+\subsection{Development of a modulation source}\label{development-of-a-modulation-source}}
 
@@
 
-\section{Methods}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 

### 2023-08-28 manuscript.tex
overleaf update

@@
 \documentclass{optica-article}
+\usepackage{xcolor} 
+\definecolor{darkred}{HTML}{BA1A1A}
+\definecolor{extralightgray}{HTML}{F5F5F5}
 
@@
 
+{ The following is very rough, taken from years ago when I first started writing the manuscript }
 This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).

### 2023-08-28 manuscript.tex
overleaf update

--- 2023-08-22 manuscript.tex
@@
 
+\textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }
 This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).

### 2023-09-11 manuscript.tex
Update on Overleaf.

--- 2023-08-22 manuscript.tex
@@
 \usepackage{lineno}
+\usepackage{todonotes}
 \linenumbers % Turn off line numbering for Optica Open preprint submissions.
@@
 
-\author{Author One,\authormark{1} Author Two,\authormark{2,*} and Author Three\authormark{2,3}}
+\author{Andrew Mueller\authormark{1, 2, *}, Boris Korzh\authormark{2}, Emma E.
+Wollman\authormark{2}, Ioana Craiciu\authormark{2}, Andrew D.
+Beyer\authormark{2}, Makan Mohageg\authormark{2}, {Lautaro Narv\'aez}\authormark{3},  Maria Spiropulu\authormark{3}, Matthew D.
+Shaw\authormark{2}}
 
-\address{\authormark{1}Peer Review, Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
-\authormark{2}Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
-\authormark{3}Currently with the Department of Electronic Journals, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA}
+\address{\authormark{1}Applied Physics, California Institute of Technology, 1200 E California Blvd., Pasadena, CA, 91125, USA \\
+\authormark{2}Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA, 91109, USA\\
+\authormark{3}Division of Physics, Mathematics and Astronomy, California Institute of Technology, 1200 E California Blvd., Pasadena, CA 91125, USA}
 
-\email{\authormark{*}opex@optica.org} %% email address is required; see note below about the corresponding author designation
-
-% use {asbstract*} to suppress the copyright line. Copyright information will be added in production
+\email{\authormark{*}amueller@caltech.edu} %% email address is required; see note below about the corresponding author designation
 
@@
 Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors.
-If leveraged to it's full potential, PNR capabilty can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing.
-Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors.
-In this work we put a differential readout SNSPD to the ultimate test.
-We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
+If leveraged to it's full potential, PNR capability can have a profound impact on the utility of SNSPDs in certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing.
+Discrimination of not just photon number but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors.
+In this work we test a PNR detector's response in a Pulse Position Modulation (PPM) experiment whereby classical data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
 We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
-We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
+We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time and photon number.
 \end{abstract*}
@@
 
-This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
+\textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }
+This study aimed to evaluate the feasibility of transmitting high clock-rate PPM data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
 The investigation was driven by recent advancements in NbN SNSPDs, which have achieved a jitter as low as 50 ps at the FW(1/100)M level, enabling the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
@@
 
+\hypertarget{Detector metrics for high-rate photon detection}{%
+\section{Detector figure of merit}
+\label{fom}}
+
+The work here highlights the application of low jitter single-photon detectors for optical communication, which is impactful for deep-space optical communication as well as classical communication in quantum networks.
+Although single-photon counting is well estanblished for deep-space optical communication~\cite{Laser lunar, DSOC} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs.
+However, with the eachievement of high data rates recently achieved with photon-counting classical communication, these approaches can now be seriously considered for quantum networks.
+The main driver is would be the deduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel~\cite{EraerdsRaman}
+\todo[inline]{Calculate reduction in power from state of the art SFP modules}
+
+To access the applicability of different detectors, here we compare some of the recent near infrared detectors.
+
+A useful figure of merit that includes all of the revelant detector metrics for photon timing was introduced by Bronzi and co-authors\cite{Bronzi2016}
+
+$$FoM_T = \frac{\eta  (1 - P_{ap})\Phi_{-3 \text{dB}}}{J} \sqrt{\frac{A}{D}},$$
+
+where $\eta$ is the single photon detection efficiency, $\Phi_{-3 \text{dB}}$ is the photon flux at which the system detection efficiency drops by 3~dB, $P_{ap}$ is the afterpulsing probability, $J$ is the detector jitter evaluated as the FWHM, $T_d$ is the deadtime, $A$ is the active area and $D$ is the dark count rate.
+Here we have defined the maximum photon flux as the 3~dB point, for ease of standardization.
+
+In this work:
+\begin{itemize}
+    \item Efficiency = 0.84
+    \item Afterpulsing = 0 \%
+    \item Jitter = 15 ps
+    \item Deadtime = 30 ns \todo[inline]{measure 3dB flux}
+    \item Area = 330 $\mu m^2$
+    \item Dark count rate = 20 Hz
+\end{itemize}
+$FoM_T = 7.58 \times 10^{12}$ at 1550 nm.
+
+The deadtime is calculated as the 1/MCR, which is the 3 dB point of the nominal efficiency.
+This is only a factor of 3.7 less than the state of the art visible Silicon SPADs (peak efficiency at 480~nm) ~\cite{Gramuglia2022}.
+
+In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays.
+Recently published high-count rate arrays have figures of merit of \todo[inline]{$FoM_T$ for Peacoq and Resta2023 results}.
+This would result a proportinal increase in the data rate.
+\todo[inline]{$FoM_T$ for fastest InGaAs/InP gated detector}.
+These devices are ideal for fiber-based optical communication. In free-space, the active area is especially important, whithout the use of an adaptive optics system.
+\todo[inline]{$FoM_T$ for DSOC array}.
+
 \hypertarget{methods}{%

### 2023-09-11 manuscript.tex
overleaf update

--- 2023-08-28 manuscript.tex
@@
 Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors.
-If leveraged to it's full potential, PNR capabilty can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing.
+If leveraged to it's full potential, PNR capability can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing.
 Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors.
@@
 
-{ The following is very rough, taken from years ago when I first started writing the manuscript }
+\textcolor{green}{ The following is very rough, taken from years ago when I first started writing the manuscript }
+
 This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).

### 2023-09-22 manuscript.tex
Update on Overleaf.

@@
 
-\textcolor{green}{ The following is very rough, taken from years ago when I first started writing the manuscript }
+\textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }
 
@@
 
+\hypertarget{detector-figure-of-merit}{%
+\section{Detector Figure of Merit}\label{detector-figure-of-merit}}
+
+The work here highlights the application of low jitter single-photon detectors for optical communication, which is impactful for deep-space optical communication as well as classical communication in quantum networks.
+Although single-photon counting is well estanblished for deep-space optical communication\textasciitilde{}\cite{Laser lunar, DSOC} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs.
+However, with the eachievement of high data rates recently achieved with photon-counting classical communication, these approaches can now be seriously considered for quantum networks.
+The main driver is would be the deduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
+\textcolor{red}{Calculate reduction in power from state of the art SFP modules}
+
+To access the applicability of different detectors, here we compare some of the recent near infrared detectors.
+
+A useful figure of merit that includes all of the revelant detector metrics for photon timing was introduced by Bronzi and co-authors \cite{Bronzi2016}
+
+\[FoM_T = \frac{\eta  (1 - P_{ap})\Phi_{-3 \text{dB}}}{J} \sqrt{\frac{A}{D}},\]
+
+where \(\eta\) is the single photon detection efficiency, \(\Phi_{-3 \text{dB}}\) is the photon flux at which the system detection efficiency drops by 3\textasciitilde dB, \(P_{ap}\) is the afterpulsing probability, \(J\) is the detector jitter evaluated as the FWHM, \(T_d\) is the deadtime, \(A\) is the active area and \(D\) is the dark count rate.
+Here we have defined the maximum photon flux as the 3\textasciitilde dB point, for ease of standardization.
+
+In this work:
+
+\begin{itemize}
+\tightlist
+\item
+  Efficiency = 0.84
+\item
+  Afterpulsing = 0 \%
+\item
+  Jitter = 15 ps
+\item
+  Deadtime = 30 ns \textcolor{red}{measure 3dB flux}
+\item
+  Area = 330 \(\mu m^2\)
+\item
+  Dark count rate = 20\Hz
+\end{itemize}
+
+\(FoM_T = 7.58 \times 10^{12}\) at 1550 nm.
+
+The deadtime is calculated as the 1/MCR, which is the 3 dB point of the nominal efficiency.
+This is only a factor of 3.7 less than the state of the art visible Silicon SPADs (peak efficiency at 480\nm) \cite{Gramuglia2022}
+
+In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays.
+Recently published high-count rate arrays have figures of merit of \textcolor{red}{\(FoM_T\) for Peacoq and Resta2023 results}.
+This would result in a proportinal increase in the data rate.
+\textcolor{red}{\(FoM_T\) for fastest InGaAs/InP gated detector}
+These devices are ideal for fiber-based optical communication. In free-space, the active area is especially important, whithout the use of an adaptive optics system.
+\textcolor{red}{\(FoM_T\) for DSOC array}
+
 \hypertarget{development-of-a-modulation-source}{%
@@
 
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+results here
+
 \bibliography{references}

### 2023-09-23 manuscript.tex
overleaf update

@@
 Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors.
-In this work we put a differential readout SNSPD to the ultimate test.
-We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
+In this work we test a differential readout SNSPD in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
 We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
-We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
+We find that cluster analysis and gaussian mixture models are useful for extracting precise measurements of pulse arrival time and photon number.
 \end{abstract*}
@@
 This technique is considered essential for future low-jitter applications of SNSPDs that exhibit photon-number effects.
+
+\hypertarget{fig:figurename2}{%
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{./figs_03/fig_intro_light.pdf}
+\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation.
+An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data.
+b) Diagram of the expiremental setup.
+WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
+\label{fig:figurename2}
+\end{figure}
+}
 
@@
 \item
-  Dark count rate = 20\Hz
+  Dark count rate = 20~Hz
 \end{itemize}
@@
 
-This is the methods section with some latex \(\frac{33}{44}\)
-
-Here is citation \cite{Dolinar2011Photon} and here is the rest of the sentence.
-
 \hypertarget{results}{%

### 2023-09-23 manuscript.tex
overleaf update

@@
 
-\hypertarget{fig:figurename2}{%
+\hypertarget{fig:intro}{%
 \begin{figure}
 \centering
-\includegraphics[width=0.7\textwidth]{./figs_03/fig_intro_light.pdf}
+\includegraphics[width=0.8\textwidth]{./figs_03/fig_intro_light.pdf}
 \caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation.
@@
 WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
-\label{fig:figurename2}
+\label{fig:intro}
 \end{figure}
@@
 This is possible with the use of low jitter detection systems or low jitter superconducting nanowire single-photon detectors (SNSPDs).
+
+\hypertarget{fig:waveform}{%
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{./figs_03/waveform_light.pdf}
+\caption[{PNR-sensitive Pulse Waveform}]{\textbf{PNR-sensitive Pulse Waveform} The rising edge of the differential SNSPD's RF pulses exibit variations in height, slew rate, and arrival time due to photon-number dependent dynamics.
+The slopes of the 1-photon and 2-photon pulses significantly differ, and as the photon number increases, the alterations to the pulse shape become progressively smaller.
+Trigger levels A (8~mV) and B (50~mV) were used to extract as much information about pulse slope and arrival time as possible}
+\label{fig:waveform}
+\end{figure}
+}
 

### 2023-09-29 manuscript.tex
Update on Overleaf.
overleaf update

@@
 Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors.
-In this work we test a differential readout SNSPD in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
+In this work we put a differential readout SNSPD to the ultimate test.
+We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
 We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
-We find that cluster analysis and gaussian mixture models are useful for extracting precise measurements of pulse arrival time and photon number.
+We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
 \end{abstract*}
@@
 \textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }
+
+\protect\hypertarget{..ux2fcodeux2ftest_1}{}{}
 
@@
 
+\hypertarget{slope-correction}{%
+\subsection{Slope Correction}\label{slope-correction}}
+
+\hypertarget{fig:slope-correction}{%
+\begin{figure}
+\centering
+\includegraphics[width=0.75\textwidth]{./figs_03/slope_cancellation_light.pdf}
+\caption[{PNR Slope Variation Analysis and Cancellation}]{\textbf{PNR Slope Variation Analysis and Cancellation} a) 2D histogram of RF pulse measurements.
+Through graphing slope \(\Delta t_{BA}\) on the x-axis and arrival time \(t_A\) on the y-axis, a series of groupings are visible that identify the discrete photon numbers detected.}
+\label{fig:slope-correction}
+\end{figure}
+}
+
+\hypertarget{cluster-analysis}{%
+\subsection{Cluster Analysis}\label{cluster-analysis}}
+
 \hypertarget{results}{%

### 2023-10-02 manuscript.tex
overleaf update

@@
 
-\textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }
-
-\protect\hypertarget{..ux2fcodeux2ftest_1}{}{}
+{}
 
@@
 The main driver is would be the deduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
-\textcolor{red}{Calculate reduction in power from state of the art SFP modules}
+{Calculate reduction in power from state of the art SFP modules}
 
@@
 \item
-  Deadtime = 30 ns \textcolor{red}{measure 3dB flux}
+  Deadtime = 30 ns {measure 3dB flux}
 \item
@@
 In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays.
-Recently published high-count rate arrays have figures of merit of \textcolor{red}{\(FoM_T\) for Peacoq and Resta2023 results}.
+Recently published high-count rate arrays have figures of merit of {\(FoM_T\) for Peacoq and Resta2023 results}.
 This would result in a proportinal increase in the data rate.
-\textcolor{red}{\(FoM_T\) for fastest InGaAs/InP gated detector}
+{\(FoM_T\) for fastest InGaAs/InP gated detector}
 These devices are ideal for fiber-based optical communication. In free-space, the active area is especially important, whithout the use of an adaptive optics system.
-\textcolor{red}{\(FoM_T\) for DSOC array}
+{\(FoM_T\) for DSOC array}
 

### 2023-10-05 manuscript.tex
overleaf update

--- 2023-09-29 manuscript.tex
@@
 \begin{abstract*} 
-Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors.
-If leveraged to it's full potential, PNR capability can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing.
-Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors.
-In this work we put a differential readout SNSPD to the ultimate test.
-We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock.
-We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses.
-We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
+Superconducting Nanowire Single Photon Detectors are a type of time-correlated photon detector with low jitter performance especially in the mid-infrared.
+They are useful for classical communication over high loss channels --such as across deep space-- and for quantum communication for which signals are restricted to the few-photon level.
+For classical communication, high photon information efficiency communication may be achieved with Pulse Position Modulation (PPM) whereby data is encoded in the arrival time of an optical pulse with respect to a clock.
+In the process of demonstrating PPM on a 20~Ghz clock, we study the effects of Photon Number Resolution (PNR) in new low-jitter types of SNSPDs.
+These PNR effects complicate fixed-threshold triggering of RF pulses from the SNSPD, and corrupt arrival time measurements if not properly managed.
+We demonstrate methods for simultaneous arrival time and photon number measurement which enables high clock rate PPM for space applications as well as high rate quantum communication and computing applications that benefit from photon number resolution.
 \end{abstract*}
@@
 
-\textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }
+Deep Space Optical Communication has been a growing field of study in recent years, as researchers look for ways to communicate with spacecraft that are far away from Earth.
+The main challenge in deep space optical communication is the high loss and distance that the link must traverse.
+This limits the communication from the spacecraft, as it is limited by the power available on the spacecraft.
+This means that the communication protocol is limited by the number of bits that can be sent per unit of energy on the spacecraft, also known as photon information efficiency or bits per photon.
 
-\protect\hypertarget{..ux2fcodeux2ftest_1}{}{}
+In this article, we will focus on the use of Pulse Position Modulation (PPM) for deep space optical communication.
+PPM can achieve higher photon information efficiency than coherent detection techniques {[}cite a method here, like is QAM one of them?
+See dolinar paper{]} for which the need to measure phase of the incoming optical signal limits minimum transmission power.
 
-This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
-The investigation was driven by recent advancements in NbN SNSPDs, which have achieved a jitter as low as 50 ps at the FW(1/100)M level, enabling the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
-The aim was to increase the data rate by a factor of 10, from 2 GHz to 20 GHz, in the next generation of the Deep Space Optical Communication (DSOC) project.
+PPM involves sending an optical pulse in one of \(2^M\) possible time slots. The transmissio of each such pulse carries M bits of information.
 
-During the course of this study, the focus shifted towards investigating the impact of photon number resolution (PNR) on the low jitter detection of optical pulses.
-PNR can have an unintended impact on the demonstration of high-rate PPM, and therefore a thorough study of its effects was deemed crucial.
-A novel PNR cancellation technique was developed and applied to successfully demonstrate high-rate PPM.
-This technique is considered essential for future low-jitter applications of SNSPDs that exhibit photon-number effects.
+For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
+The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \todo[inline]{XX to XX} Au.
 
-This study aimed to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
+For large M, PPM achieves high photon information efficiency, allowing for the saving of power on the spacecraft and the sending of more information with fewer photons.
+The existing deep space optical communication project uses M up to \(2^8 = 256\), meaning that 8 bits of data are carried in each optical pulse.
+
+In this project, we aimed to demonstrate even higher photon information efficiency by using M values up to 2048, or 11 bits of data per optical pulse.
+
+While the use of large M values increases photon information efficiency, it also decreases the data rate of the system.
+This is because the number of time bins needed per optical pulse scales exponentially with the amount of data in each pulse.
+Therefore, for a given fixed clock rate and time bin duration, the data rate decreases dramatically for higher M values.
+
+Using M values much larger than 11 is unlikely to be practical in future deep space optical communication systems.
+However, the data rate of these systems can be increased linearly by increasing the clock rate or bin size of the experiment.
+This is possible with the use of low jitter detection systems or low jitter superconducting nanowire single-photon detectors (SNSPDs).
+
+This study aims to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
 The investigation was driven by recent advancements in NbN SNSPDs, which have achieved a jitter as low as 50 ps at the FW(1/100)M level, enabling the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
@@
 
-\hypertarget{pulse-position-modulation-for-deep-space-communication}{%
-\subsection{Pulse Position Modulation for Deep Space Communication}\label{pulse-position-modulation-for-deep-space-communication}}
-
-Deep Space Optical Communication has been a growing field of study in recent years, as researchers look for ways to communicate with spacecraft that are far away from Earth.
-In this article, we will focus on the use of Pulse Position Modulation (PPM) for deep space optical communication.
-
-While other modulation techniques such as quadrature amplitude modulation (QAM) have been used in the past, it has been shown that in the photon-starved regime, PPM is the best approach for sending data.
-This is because there is not enough light to measure the phase of the signal.
-
 PPM relies on sending one optical pulse carrying M bits of information in one of \(2^M\) possible time slots.
@@
 
-The main challenge in deep space optical communication is the high loss and distance that the link must traverse.
-This limits the communication from the spacecraft, as it is limited by the power available on the spacecraft.
-This means that the communication protocol is limited by the number of bits that can be sent per unit of energy on the spacecraft, also known as photon information efficiency or bits per photon.
-
-For large M, PPM achieves high photon information efficiency, allowing for the saving of power on the spacecraft and the sending of more information with fewer photons.
-The existing deep space optical communication project uses M up to \(2^8 = 256\), meaning that 8 bits of data are carried in each optical pulse.
-
-In this project, we aimed to demonstrate even higher photon information efficiency by using M values up to 2048, or 11 bits of data per optical pulse.
-
-While the use of large M values increases photon information efficiency, it also decreases the data rate of the system.
-This is because the number of time bins needed per optical pulse scales exponentially with the amount of data in each pulse.
-Therefore, for a given fixed clock rate and time bin duration, the data rate decreases dramatically for higher M values.
-
-Using M values much larger than 11 is unlikely to be practical in future deep space optical communication systems.
-However, the data rate of these systems can be increased linearly by increasing the clock rate or bin size of the experiment.
-This is possible with the use of low jitter detection systems or low jitter superconducting nanowire single-photon detectors (SNSPDs).
+\hypertarget{section}{%
+\section{--------------------}\label{section}}
 

### 2023-10-05 manuscript.tex
overleaf update

@@
 For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
-The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \todo[inline]{XX to XX} Au.
+The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \todo[inline]{XX to XX} Au..
 

### 2023-10-05 manuscript.tex
overleaf update

--- 2023-10-05 manuscript.tex
@@
 For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
-The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \todo[inline]{XX to XX} Au.
+The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\textcolor{red}{\hl{XX to XX} Au..
 

### 2023-10-05 manuscript.tex
overleaf update

--- 2023-10-05 manuscript.tex
@@
 For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
-The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \todo[inline]{XX to XX} Au.
+The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\textcolor{red}{\hl{XX to XX}}} Au..
 

### 2023-10-05 manuscript.tex
overleaf update

--- 2023-10-05 manuscript.tex
@@
 \usepackage{todonotes}
+\usepackage{xcolor}
+\usepackage{soul}
 \linenumbers % Turn off line numbering for Optica Open preprint submissions.
@@
 For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
-The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \todo[inline]{XX to XX} Au..
+The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}} Au..
 

### 2023-10-05 manuscript.tex
overleaf update

@@
 
-PPM involves sending an optical pulse in one of \(2^M\) possible time slots. The transmissio of each such pulse carries M bits of information.
+PPM involves sending an optical pulse in one of $2^M$ possible time slots. The transmissio of each such pulse carries M bits of information.
 
 For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
-The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}} Au..
+The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}}Au.
 
 For large M, PPM achieves high photon information efficiency, allowing for the saving of power on the spacecraft and the sending of more information with fewer photons.
-The existing deep space optical communication project uses M up to \(2^8 = 256\), meaning that 8 bits of data are carried in each optical pulse.
+The existing deep space optical communication project uses M up to $2^8 = 256$, meaning that 8 bits of data are carried in each optical pulse.
 
@@
 
-PPM relies on sending one optical pulse carrying M bits of information in one of \(2^M\) possible time slots.
+PPM relies on sending one optical pulse carrying M bits of information in one of $2^M$ possible time slots.
 For M = 2, this corresponds to sending an early pulse to represent a 0 bit and a late pulse to represent a 1 bit.
@@
 
-\[FoM_T = \frac{\eta  (1 - P_{ap})\Phi_{-3 \text{dB}}}{J} \sqrt{\frac{A}{D}},\]
+$$FoM_T = \frac{\eta  (1 - P_{ap})\Phi_{-3 \text{dB}}}{J} \sqrt{\frac{A}{D}},$$
 
-where \(\eta\) is the single photon detection efficiency, \(\Phi_{-3 \text{dB}}\) is the photon flux at which the system detection efficiency drops by 3\textasciitilde dB, \(P_{ap}\) is the afterpulsing probability, \(J\) is the detector jitter evaluated as the FWHM, \(T_d\) is the deadtime, \(A\) is the active area and \(D\) is the dark count rate.
+where $\eta$ is the single photon detection efficiency, $\Phi_{-3 \text{dB}}$ is the photon flux at which the system detection efficiency drops by 3\textasciitilde dB, $P_{ap}$ is the afterpulsing probability, $J$ is the detector jitter evaluated as the FWHM, $T_d$ is the deadtime, $A$ is the active area and $D$ is the dark count rate.
 Here we have defined the maximum photon flux as the 3\textasciitilde dB point, for ease of standardization.
@@
 \item
-  Area = 330 \(\mu m^2\)
+  Area = 330 $\mu m^2$
 \item
@@
 
-\(FoM_T = 7.58 \times 10^{12}\) at 1550 nm.
+$FoM_T = 7.58 \times 10^{12}$ at 1550 nm.
 
@@
 In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays.
-Recently published high-count rate arrays have figures of merit of \textcolor{red}{\(FoM_T\) for Peacoq and Resta2023 results}.
+Recently published high-count rate arrays have figures of merit of \textcolor{red}{$FoM_T$ for Peacoq and Resta2023 results}.
 This would result in a proportinal increase in the data rate.
-\textcolor{red}{\(FoM_T\) for fastest InGaAs/InP gated detector}
+\textcolor{red}{$FoM_T$ for fastest InGaAs/InP gated detector}
 These devices are ideal for fiber-based optical communication. In free-space, the active area is especially important, whithout the use of an adaptive optics system.
-\textcolor{red}{\(FoM_T\) for DSOC array}
+\textcolor{red}{$FoM_T$ for DSOC array}
 
@@
 \caption[{PNR Slope Variation Analysis and Cancellation}]{\textbf{PNR Slope Variation Analysis and Cancellation} a) 2D histogram of RF pulse measurements.
-Through graphing slope \(\Delta t_{BA}\) on the x-axis and arrival time \(t_A\) on the y-axis, a series of groupings are visible that identify the discrete photon numbers detected.}
+Through graphing slope $\Delta t_{BA}$ on the x-axis and arrival time $t_A$ on the y-axis, a series of groupings are visible that identify the discrete photon numbers detected.}
 \label{fig:slope-correction}

### 2023-10-05 manuscript.tex
overleaf update

@@
 For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
-The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}}Au.
+The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}} Au.
+
+\hypertarget{section}{%
+\paragraph{----}\label{section}}
 
@@
 
-\hypertarget{section}{%
-\section{--------------------}\label{section}}
+\hypertarget{section-1}{%
+\section{--------------------}\label{section-1}}
 
@@
 The main driver is would be the deduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
-\textcolor{red}{Calculate reduction in power from state of the art SFP modules}
+\textbf{\hl{Calculate reduction in power from state of the art SFP modules}}
 
@@
 \item
-  Deadtime = 30 ns \textcolor{red}{measure 3dB flux}
+  Deadtime = 30 ns \textbf{\hl{measure 3dB flux}}
 \item
@@
 The deadtime is calculated as the 1/MCR, which is the 3 dB point of the nominal efficiency.
-This is only a factor of 3.7 less than the state of the art visible Silicon SPADs (peak efficiency at 480\nm) \cite{Gramuglia2022}
+This is only a factor of 3.7 less than the state of the art visible Silicon SPADs (peak efficiency at 480~nm) \cite{Gramuglia2022}
 
 In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays.
-Recently published high-count rate arrays have figures of merit of \textcolor{red}{$FoM_T$ for Peacoq and Resta2023 results}.
+Recently published high-count rate arrays have figures of merit of \textbf{\hl{$FoM_T$ for Peacoq and Resta2023 results}}.
 This would result in a proportinal increase in the data rate.
-\textcolor{red}{$FoM_T$ for fastest InGaAs/InP gated detector}
+\textbf{\hl{$FoM_T$ for fastest InGaAs/InP gated detector}}
 These devices are ideal for fiber-based optical communication. In free-space, the active area is especially important, whithout the use of an adaptive optics system.
-\textcolor{red}{$FoM_T$ for DSOC array}
+\textbf{\hl{$FoM_T$ for DSOC array}}
 

### 2023-10-10 manuscript.tex
overleaf update

@@
 \usepackage{soul}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 \linenumbers % Turn off line numbering for Optica Open preprint submissions.
@@
 
-In this article, we will focus on the use of Pulse Position Modulation (PPM) for deep space optical communication.
-PPM can achieve higher photon information efficiency than coherent detection techniques {[}cite a method here, like is QAM one of them?
-See dolinar paper{]} for which the need to measure phase of the incoming optical signal limits minimum transmission power.
+In this article, we will focus on the use of Pulse Position Modulation (PPM) for space based optical communication.
+PPM involves sending a pulse in one of $2^M$ possible time slots.
+The transmission of each such pulse carries M bits of information based on when it arrives in a set of bins called a frame.
 
-PPM involves sending an optical pulse in one of $2^M$ possible time slots. The transmissio of each such pulse carries M bits of information.
+The Deep Space Optical Communicaiton (DSOC) project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}} Au.
 
 For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
-The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}} Au.
+This is quantified through the photon information efficiency $c_p = C/E$ where $C$ is the link capacity and $E$ is the photon cost per optical pulse
 
-\hypertarget{section}{%
-\paragraph{----}\label{section}}
+The existing deep space optical communication project uses M up to $2^8 = 256$, meaning that 8 bits of data may be carried in each optical pulse.
+M values as high as 19 have been demonstrated in the lab\cite{essiambre2023record}.
+However, the number of time bins needed per optical pulse scales exponentially with the number of bits transmitted per pulse.
+Therefore, for a given fixed clock rate and time bin duration, the PPM data rate decreases dramatically for higher M values.
 
-For large M, PPM achieves high photon information efficiency, allowing for the saving of power on the spacecraft and the sending of more information with fewer photons.
-The existing deep space optical communication project uses M up to $2^8 = 256$, meaning that 8 bits of data are carried in each optical pulse.
+We focus on demonstrating moderately large PIE, while also increasing the clock rate of the sytem by an order of magnitude relative to the DSOC platform (2\textasciitilde GHz).
+By operating at both higher clock rate and PIE than DSOC, this system exemplifies how future iterations of DSOC may send data more quickly but also over greater distances with the same power budget.
 
-In this project, we aimed to demonstrate even higher photon information efficiency by using M values up to 2048, or 11 bits of data per optical pulse.
+The increase in clock rate is made possible due to recent advancements in Niobium Nitride SNSPDs\textasciitilde{}\cite{Colangelo2023}.
+Low jitter performance is achieved by incorporating impedance matching tapers for efficient RF coupling, resulting in higher slew rate pulses, and by enabling RF pulse readout from both ends of the nanowire.
+The dual-ended readout allows for the cancellation of jitter caused by the variable location of photon arrival along the meander when the differential signals are recombined with a balun.
+These detectors acheive jitter as low as 50 ps at the FW(1/100)M level, making them suitable for the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
 
-While the use of large M values increases photon information efficiency, it also decreases the data rate of the system.
-This is because the number of time bins needed per optical pulse scales exponentially with the amount of data in each pulse.
-Therefore, for a given fixed clock rate and time bin duration, the data rate decreases dramatically for higher M values.
+However, the photon number number dependent response of these detectors is shown to affect the time-correlated measurements needed for high-rate PPM.
+This response, shown in Fig.~\ref{fig:waveform} is also known as photon number resolution (PNR) -- a property that is desirable in certain applications including quantum communication and quantum computing.
+The SNSPD generates RF pulses with greater amplitude and slew rate when detecting optical pulses with multiple photons.
+Photon number effects manifest in this lower jitter variety of SNSPD due to the more efficient coupling of the nanowire to the readout circuit through the impedance matching tapers.
+It is likely that these effects will be present in other new SNSPD types engineered for low jitter, whether the PNR resolution is desired or not.
 
-Using M values much larger than 11 is unlikely to be practical in future deep space optical communication systems.
-However, the data rate of these systems can be increased linearly by increasing the clock rate or bin size of the experiment.
-This is possible with the use of low jitter detection systems or low jitter superconducting nanowire single-photon detectors (SNSPDs).
-
-This study aims to evaluate the feasibility of transmitting high clock-rate pulse position modulated (PPM) data using a mode-locked laser and receiving it with a low jitter superconducting nanowire single-photon detector (SNSPD).
-The investigation was driven by recent advancements in NbN SNSPDs, which have achieved a jitter as low as 50 ps at the FW(1/100)M level, enabling the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
-The aim was to increase the data rate by a factor of 10, from 2 GHz to 20 GHz, in the next generation of the Deep Space Optical Communication (DSOC) project.
-
-During the course of this study, the focus shifted towards investigating the impact of photon number resolution (PNR) on the low jitter detection of optical pulses.
-PNR can have an unintended impact on the demonstration of high-rate PPM, and therefore a thorough study of its effects was deemed crucial.
-A novel PNR cancellation technique was developed and applied to successfully demonstrate high-rate PPM.
-This technique is considered essential for future low-jitter applications of SNSPDs that exhibit photon-number effects.
+As the PNR response affects the timing of fixed threashold timetaggs at any trigger level, it has a significant effect of the timing measurements used for the PPM demonstration.
+Any other applications illumnate these detectors with optical pulses of non-vanishing mean photon numbers will have to content with these effects as well.
+For this reason, we study the PNR response in detail and present two methods for managing it.
+We show how the photon number information can be deconvolved from the arrival time information, and how both de-correlated degrees of freedom can be measured simultaneously.
+This is applicable to certain types of high-rate quantum communication and computing systems.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{./figs_03/fig_intro_light.pdf}
+\includegraphics[width=0.8\textwidth]{./figs_03/fig_intro_2_light.pdf}
 \caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation.
@@
 }
-
-PPM relies on sending one optical pulse carrying M bits of information in one of $2^M$ possible time slots.
-For M = 2, this corresponds to sending an early pulse to represent a 0 bit and a late pulse to represent a 1 bit.
-
-\hypertarget{section-1}{%
-\section{--------------------}\label{section-1}}
 
@@
 \item
-  Afterpulsing = 0 \%
+  Afterpulsing = 0 %
 \item

### 2023-10-10 manuscript.tex
overleaf update

@@
 
+\hypertarget{fig:intro}{%
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{./figs_03/fig_intro_2_light.pdf}
+\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation.
+An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data.
+b) Diagram of the expiremental setup.
+WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
+\label{fig:intro}
+\end{figure}
+}
+
 However, the photon number number dependent response of these detectors is shown to affect the time-correlated measurements needed for high-rate PPM.
@@
 This is applicable to certain types of high-rate quantum communication and computing systems.
-
-\hypertarget{fig:intro}{%
-\begin{figure}
-\centering
-\includegraphics[width=0.8\textwidth]{./figs_03/fig_intro_2_light.pdf}
-\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation.
-An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data.
-b) Diagram of the expiremental setup.
-WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
-\label{fig:intro}
-\end{figure}
-}
 
@@
 
-The communication signal on a spacecraft is generated by utilizing a Continuous Wave (CW) seed laser that is carved by a fast intensity modulator.
-The resulting low-power pulsed signal is then amplified by an Erbium Doped Fiber Amplifier (EDFA) to increase its transmission power to Earth.
-The majority of the power used by the spacecraft for communication scales with the number of optical pulses due to the EDFA.
+DSOC relies on modulation of a CW seed laser to generate the communication signal on the spacecraft.
+This signal is then amplified by an Erbium Doped Fiber Amplifier (EDFA) to increase its transmission power to Earth.
+As the EDFA amplifies the pre-generated pulses and uses most of the power of the spacecraft optical transmission system, power consumption scales with the number of optical pulses.
 
-In our experiment, the 20 GHz repetition rate was limited by the jitter of the Single-Photon Detectors (SNSPDs) that we intended to use.
-These detectors have a Full Width at Half Maximum (FW(1/100)M) jitter of approximately 50 ps.
-To ensure that the response function of the entire experiment had jitter of around 50 ps FW(1/100)M, we needed to build a Pulsed Phase Modulation (PPM) source with ultra-short optical pulses.
-
-Carving a CW laser with our system would have introduced excessive timing uncertainty due to the limited ability of even the fastest lithium niobate intensity modulators to carve pulses with widths below 20 ps.
-The added jitter from modulated CW pulses, combined with the jitter of the detectors, would have exceeded the 20 GHz/50 ps slot width requirement.
+We produce our modulated singal by carving a series of mode locked laser pulses with lithium niobate modulators.
+This way, the jitter of the optical pulses themselves are not limited by the modulators or thew slew rate of the RF signal that drives them.
 

### 2023-10-10 manuscript.tex
overleaf update

@@
 
-\hypertarget{fig:intro}{%
-\begin{figure}
-\centering
-\includegraphics[width=0.8\textwidth]{./figs_03/fig_intro_2_light.pdf}
-\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation.
-An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data.
-b) Diagram of the expiremental setup.
-WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
-\label{fig:intro}
-\end{figure}
-}
+\includegraphics[width=1\textwidth]{./figs_03/fig_intro_2_light.pdf}
 

### 2023-10-10 manuscript.tex
overleaf update

@@
 
+\hypertarget{fig:intro}{%
+\begin{figure}
+\centering
 \includegraphics[width=1\textwidth]{./figs_03/fig_intro_2_light.pdf}
+\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) Diagram of the expiremental setup.
+WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp b) How bits are transmitted in M=16 PPM modulation.
+An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data.
+c) XXXXXXXX}
+\label{fig:intro}
+\end{figure}
+}
 

### 2023-10-10 manuscript.tex
overleaf update

@@
 
-\author{Author One,\authormark{1} Author Two,\authormark{2,*} and Author Three\authormark{2,3}}
+\author{Andrew Mueller\authormark{1, 2, *}, Boris Korzh\authormark{2}, Emma Wollman\authormark{2}, Andrew D. Beyer\authormark{2}, Matthew D. Shaw\authormark{2}, and Maria Spiropulu\authormark{3}}
 
-\address{\authormark{1}Peer Review, Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
-\authormark{2}Publications Department, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
-\authormark{3}Currently with the Department of Electronic Journals, Optica Publishing Group, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA}
+\address{\authormark{1}Applied Physics, California Institute of Technology, 1200 E California Blvd., Pasadena, CA, 91125, USA \\
+\authormark{2}Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA, 91109, USA \\
+\authormark{3}Division of Physics, Mathematics and Astronomy, California Institute of Technology, 1200 E California Blvd., Pasadena, CA 91125, USA }
 
-\email{\authormark{*}opex@optica.org} %% email address is required; see note below about the corresponding author designation
+\email{\authormark{*}andrewstermueller@gmail.com} %% email address is required; see note below about the corresponding author designation
 
@@
 An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data.
-c) XXXXXXXX}
+c) \textbf{\hl{XXXXXXXX}}}
 \label{fig:intro}

### 2023-10-18 manuscript.tex
overleaf update

@@
 
-Deep Space Optical Communication has been a growing field of study in recent years, as researchers look for ways to communicate with spacecraft that are far away from Earth.
-The main challenge in deep space optical communication is the high loss and distance that the link must traverse.
-This limits the communication from the spacecraft, as it is limited by the power available on the spacecraft.
-This means that the communication protocol is limited by the number of bits that can be sent per unit of energy on the spacecraft, also known as photon information efficiency or bits per photon.
+Deep space optical communication has been a growing field of study in recent years, as researchers look for ways to communicate with spacecraft that are far away from Earth.
+A key challenge in the development of this technology is closing the communication link over extremely large distances and high loss.
+This must be done given a restricted power budget available on the spacecraft, and therefore requires the use of highly efficient optical communication protocols that optimize the number of bits sent per unit of energy.
 
@@
 
-The Deep Space Optical Communicaiton (DSOC) project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}} Au.
+The Deep Space Optical Communicaiton (DSOC) project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of up to \textbf{\hl{XX}} Au.
 
-For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth.
+For larger M, more data may be sent with a single optical pulse, thereby allowing a power limited spacecraft to send more data over a high loss optical channel back to earth.
 This is quantified through the photon information efficiency $c_p = C/E$ where $C$ is the link capacity and $E$ is the photon cost per optical pulse
 
-The existing deep space optical communication project uses M up to $2^8 = 256$, meaning that 8 bits of data may be carried in each optical pulse.
-M values as high as 19 have been demonstrated in the lab\cite{essiambre2023record}.
-However, the number of time bins needed per optical pulse scales exponentially with the number of bits transmitted per pulse.
+The existing DSOC project uses M up to $2^8 = 256$, meaning 8 bits of data may be carried in each optical pulse.
+M values as high as 19 have been demonstrated in the lab~\cite{essiambre2023record}, but the number of time bins needed per frame scales exponentially with the number of bits transmitted per pulse.
 Therefore, for a given fixed clock rate and time bin duration, the PPM data rate decreases dramatically for higher M values.
 
-We focus on demonstrating moderately large PIE, while also increasing the clock rate of the sytem by an order of magnitude relative to the DSOC platform (2\textasciitilde GHz).
+We demonstrate a high clock rate PPM protocol in the lab based on modulating a mode-locked laser and receiving pulses with a low jitter superconducting nanowire single photon detector (SNSPD) (fig.~\ref{fig:intro} (a)).We focus on demonstrating moderately large PIE, while also increasing the clock rate of the sytem by an order of magnitude relative to the DSOC platform (2\textasciitilde GHz).
 By operating at both higher clock rate and PIE than DSOC, this system exemplifies how future iterations of DSOC may send data more quickly but also over greater distances with the same power budget.
 
-The increase in clock rate is made possible due to recent advancements in Niobium Nitride SNSPDs\textasciitilde{}\cite{Colangelo2023}.
-Low jitter performance is achieved by incorporating impedance matching tapers for efficient RF coupling, resulting in higher slew rate pulses, and by enabling RF pulse readout from both ends of the nanowire.
+The rate increase is possible due to recent advancements in Niobium Nitride SNSPDs~\cite{Colangelo2023}.
+These acheive low jitter performance by incorporating impedance matching tapers for efficient RF coupling, resulting in higher slew rate pulses, and by enabling RF pulse readout from both ends of the nanowire.
 The dual-ended readout allows for the cancellation of jitter caused by the variable location of photon arrival along the meander when the differential signals are recombined with a balun.
-These detectors acheive jitter as low as 50 ps at the FW(1/100)M level, making them suitable for the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
+These detectors achieve jitter as low as 50 ps at the FW(1/100)M level, making them suitable for the demonstration of PPM with 50 ps slot widths and a 20 GHz clock.
 
@@
 The work here highlights the application of low jitter single-photon detectors for optical communication, which is impactful for deep-space optical communication as well as classical communication in quantum networks.
-Although single-photon counting is well estanblished for deep-space optical communication\textasciitilde{}\cite{Laser lunar, DSOC} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs.
+Although single-photon counting is well estanblished for deep-space optical communication~\cite{Laser lunar, DSOC} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs.
 However, with the eachievement of high data rates recently achieved with photon-counting classical communication, these approaches can now be seriously considered for quantum networks.
@@
 
+{}
+
 \bibliography{references}

### 2023-10-18 manuscript.tex
overleaf update

@@
 
-We demonstrate a high clock rate PPM protocol in the lab based on modulating a mode-locked laser and receiving pulses with a low jitter superconducting nanowire single photon detector (SNSPD) (fig.~\ref{fig:intro} (a)).We focus on demonstrating moderately large PIE, while also increasing the clock rate of the sytem by an order of magnitude relative to the DSOC platform (2\textasciitilde GHz).
+We demonstrate a high clock rate PPM protocol in the lab based on modulating a mode-locked laser and receiving pulses with a low jitter superconducting nanowire single photon detector (SNSPD) (fig.~\ref{fig:intro} (a)).We focus on demonstrating moderately large PIE, while also increasing the clock rate of the sytem by an order of magnitude relative to the DSOC platform (2~GHz).
 By operating at both higher clock rate and PIE than DSOC, this system exemplifies how future iterations of DSOC may send data more quickly but also over greater distances with the same power budget.
@@
 
-where $\eta$ is the single photon detection efficiency, $\Phi_{-3 \text{dB}}$ is the photon flux at which the system detection efficiency drops by 3\textasciitilde dB, $P_{ap}$ is the afterpulsing probability, $J$ is the detector jitter evaluated as the FWHM, $T_d$ is the deadtime, $A$ is the active area and $D$ is the dark count rate.
-Here we have defined the maximum photon flux as the 3\textasciitilde dB point, for ease of standardization.
+where $\eta$ is the single photon detection efficiency, $\Phi_{-3 \text{dB}}$ is the photon flux at which the system detection efficiency drops by 3~dB, $P_{ap}$ is the afterpulsing probability, $J$ is the detector jitter evaluated as the FWHM, $T_d$ is the deadtime, $A$ is the active area and $D$ is the dark count rate.
+Here we have defined the maximum photon flux as the 3~dB point, for ease of standardization.
 

### 2023-10-19 manuscript.tex
overleaf update

@@
 \includegraphics[width=0.8\textwidth]{./figs_03/waveform_light.pdf}
-\caption[{PNR-sensitive Pulse Waveform}]{\textbf{PNR-sensitive Pulse Waveform} The rising edge of the differential SNSPD's RF pulses exibit variations in height, slew rate, and arrival time due to photon-number dependent dynamics.
+\caption[{PNR-sensitive Pulse Waveform}]{\textbf{PNR-sensitive Pulse Waveform} The rising edge of the differential SNSPD's RF pulses exhibit variations in height, slew rate, and arrival time due to photon-number dependent dynamics.
 The slopes of the 1-photon and 2-photon pulses significantly differ, and as the photon number increases, the alterations to the pulse shape become progressively smaller.

### 2023-10-22 manuscript.tex
overleaf update

@@
 
-Deep space optical communication has been a growing field of study in recent years, as researchers look for ways to communicate with spacecraft that are far away from Earth.
+Deep space optical communication has been a growing field of study in recent years, as space agencies look for ways to increase data rates to and from deep space missions.
 A key challenge in the development of this technology is closing the communication link over extremely large distances and high loss.
-This must be done given a restricted power budget available on the spacecraft, and therefore requires the use of highly efficient optical communication protocols that optimize the number of bits sent per unit of energy.
+This must be done given a restricted power budget available on the spacecraft, and therefore requires the use of photon efficient communication protocols that optimize the number of bits sent per unit of energy.
 
-In this article, we will focus on the use of Pulse Position Modulation (PPM) for space based optical communication.
-PPM involves sending a pulse in one of $2^M$ possible time slots.
-The transmission of each such pulse carries M bits of information based on when it arrives in a set of bins called a frame.
+In this article, we demonstrate high rate Pulse Position Modulation (PPM) applicable to future deep space communication.
+This starts with a transmitter that sends an optical pulse in one of $2^M$ possible time slots measured with respect to a clock.
+At a receiver, the arrival time of this pulse is measured to recover $M$ bits of encoded data.
+Each successive set of $2^M$ time slots following by a dead time constitute a PPM frame.
 
-The Deep Space Optical Communicaiton (DSOC) project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of up to \textbf{\hl{XX}} Au.
+The Deep Space Optical Communicaiton (DSOC) project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of 0.06 to 2.7 Au \cite{Srinivasan2023GroundReceiver}.
 
@@
 
-The existing DSOC project uses M up to $2^8 = 256$, meaning 8 bits of data may be carried in each optical pulse.
+The DSOC project uses M at least as high as 5, meaning 5 bits of data are send using 32 time slots per frame.
 M values as high as 19 have been demonstrated in the lab~\cite{essiambre2023record}, but the number of time bins needed per frame scales exponentially with the number of bits transmitted per pulse.
@@
 The rate increase is possible due to recent advancements in Niobium Nitride SNSPDs~\cite{Colangelo2023}.
-These acheive low jitter performance by incorporating impedance matching tapers for efficient RF coupling, resulting in higher slew rate pulses, and by enabling RF pulse readout from both ends of the nanowire.
+These achieve low jitter performance by incorporating impedance matching tapers for efficient RF coupling, resulting in higher slew rate pulses, and by enabling RF pulse readout from both ends of the nanowire.
 The dual-ended readout allows for the cancellation of jitter caused by the variable location of photon arrival along the meander when the differential signals are recombined with a balun.
@@
 
-However, the photon number number dependent response of these detectors is shown to affect the time-correlated measurements needed for high-rate PPM.
-This response, shown in Fig.~\ref{fig:waveform} is also known as photon number resolution (PNR) -- a property that is desirable in certain applications including quantum communication and quantum computing.
+However, these detectors exhibit photon number number dependent responses that affect the time-correlated measurements needed for high-rate PPM.
+This behavior, shown in Fig.~\ref{fig:waveform} is also known as photon number resolution (PNR) -- a property that is desirable in certain applications including quantum communication and quantum computing.
 The SNSPD generates RF pulses with greater amplitude and slew rate when detecting optical pulses with multiple photons.
-Photon number effects manifest in this lower jitter variety of SNSPD due to the more efficient coupling of the nanowire to the readout circuit through the impedance matching tapers.
-It is likely that these effects will be present in other new SNSPD types engineered for low jitter, whether the PNR resolution is desired or not.
+Photon number effects are especially evident in this lower jitter variety of SNSPD due to the use of impedance matching tapers which more efficiently couple energy out of the nanowire and into the readout circuit.
+With high resolution time tagging equipment, photon number dependent effects have even been observed in SNSPDs not necessarily designed to exhibit it \citep[\cite{sauer2023resolving}]{schapeler2023superconducting} like those without tapers \cite{Cahall2017SlewRatePNR}.
+Therefore it is increasingly likely that future research involving low-jitter SNSPDs and multiphoton pulsed sources will have to explicitly manage the PNR response for accurate time-correlated measurements -- whether the effect it is desired or not.
 
-As the PNR response affects the timing of fixed threashold timetaggs at any trigger level, it has a significant effect of the timing measurements used for the PPM demonstration.
-Any other applications illumnate these detectors with optical pulses of non-vanishing mean photon numbers will have to content with these effects as well.
-For this reason, we study the PNR response in detail and present two methods for managing it.
-We show how the photon number information can be deconvolved from the arrival time information, and how both de-correlated degrees of freedom can be measured simultaneously.
-This is applicable to certain types of high-rate quantum communication and computing systems.
+For the tapered differential detectors, the PNR response affects timing of fixed threshold timetaggs at any trigger level (fig.~\ref{fig:waveform}).
+However, at higher trigger levels the PNR response is less pronounced and the timing measurements are less affected.
+Therefore, we divide a single SNSPD readout line using an RF splitter and trigger on the RF pulse at a high and low level as shwon by the red lines in fig.~\ref{fig:waveform}.
+This allows us to extract the somewhat conjugate information of pulse arrival time and photon number.
+From these measurements we study the PNR response in detail and present two methods for managing it.
+We demonstrate how the photon number information may be deconvolved from the arrival time information, and how both de-correlated degrees of freedom can be extracted simultaneously.
+This enables the original goal of high rate PPM, but also informs how low-jitter photon number resolving SNSPDs can be used in other classical communication and quantum applications.
 
@@
 The work here highlights the application of low jitter single-photon detectors for optical communication, which is impactful for deep-space optical communication as well as classical communication in quantum networks.
-Although single-photon counting is well estanblished for deep-space optical communication~\cite{Laser lunar, DSOC} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs.
+Although single-photon counting is well estanblished for deep-space optical communication~\cite{Srinivasan2023GroundReceiver} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs.
 However, with the eachievement of high data rates recently achieved with photon-counting classical communication, these approaches can now be seriously considered for quantum networks.
-The main driver is would be the deduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
+The main driver is the reduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
 \textbf{\hl{Calculate reduction in power from state of the art SFP modules}}
@@
 
-We produce our modulated singal by carving a series of mode locked laser pulses with lithium niobate modulators.
-This way, the jitter of the optical pulses themselves are not limited by the modulators or thew slew rate of the RF signal that drives them.
+We produce our PPM signal signal by carving a high rate mode locked laser with lithium niobate modulators.
+This way, the jitter of the optical pulses themselves are not limited by the modulators or slew slew rate of the RF signal that drives them.
+We do two PPM demonstrations, with the source mode locked laser operating at 10.75 and 20 GHz.
+THe 10.75 GHz demonstration uses a M value of 10, thereby making frames with 1024 time slots of 93 ps width each.
+The 20 GHz demonstration uses M=11, giving 2048 time slots of 50 ps width per frame.
+Each frame ends with a dead time of approximately 150 ns to allow the SNSPD to fully recover before the next frame.
 
-Therefore, we chose to carve pulses from a mode-locked laser.
-This approach allows for extremely short pulses in time, with the modulators responsible for sufficiently reducing any surrounding unwanted pulses.
-The temporal width of the modulator pulse response must be extremely short and able to modulate from `off' to `on' within a time frame of the order of the 50 ps bin width.
+Several modern free running time taggers support the averaging of multiple input channels to create fewer higher resolution channels.
+This implies a tradeoff between jitter or timing resolution and number of channels for a given time tagging device.
+Therefore, it is important to consider readout methods like that presented here that make use of 2 lower-resolution channels in place of a single higher resolution channel, as these two configurations are similarly resource efficient.
 
@@
 
-\hypertarget{slope-correction}{%
-\subsection{Slope Correction}\label{slope-correction}}
+Prior to the PPM demosntration, we collected data with multi-photon optical pulses repeatedly impinging on the detector at the same time with respect to a clock.
+This way, we study how the PNR effect in isolation is manifest in the timing measurements recorded at the low and high trigger levels.
+We label the measurements from the low (8~mV) and high (50~mV) trigger levels as $t_A$ and $t_B$ respectively.
+As shown in fig.~\ref{fig:waveform}, histograms of these arrival events are multimodal due to the PNR response.
+We first present a method for recovering a symmetric arrival time response function using the the slope measurement $\Delta t_{BA} = t_B - t_A$.
 
-\hypertarget{fig:slope-correction}{%
+\hypertarget{slope-based-correction}{%
+\subsection{Slope-Based Correction}\label{slope-based-correction}}
+
+\hypertarget{fig:slope_correction}{%
 \begin{figure}
@@
 Through graphing slope $\Delta t_{BA}$ on the x-axis and arrival time $t_A$ on the y-axis, a series of groupings are visible that identify the discrete photon numbers detected.}
-\label{fig:slope-correction}
+\label{fig:slope_correction}
 \end{figure}
 }
+
+Pairs of pulse measurements $t_A$ and $t_B$ may be graphed on a 2D plane parametrized by $\Delta t_{BA}$ on the x-axis and $t_A$.
+fig.~\ref{fig:slope_correction} a shows how this protection exhibits multiple groupings that correspond the the photon number character of the impinging optical mode.
+The 1 and 2-photon events are clearly identifiable and seperated from other events, with $|3\rangle$, $|4\rangle$, and $|5\rangle$ events also visible with less mutual separation.
+While fig.~\ref{fig:slope_correction} a is shown here for just one mean photon number $\mu$, these grouplings are collected for a full range of attenuations and corresponding $\mu$.
+fig.~\ref{fig:slope_correction} a shows histograms from projecting 3 such groupings down onto the $\Delta t_{BA}$ axis.
+
+Thee slope correction method involves the measurement and creation of a slope-versus-arrival time line, one of which is shown in fig.~\ref{fig:slope_correction} a.
+This is produced by averaging all $t_A$ measurements for a given slope $\Delta t_{BA}$.
+That is, the values along vertical slices of the 2D density plot in fig.~\ref{fig:slope_correction} a are averaged to produce the y-coordinates of the slope-versus-arrival time line shown in black.
+By interpolating new $\Delta t_{BA}$ measurements on this curve and using it like a lookup table, PNR corrections $C_A$ are found.
+These may be subtracted off from $t_A$ producting $\tilde{t_A} = t_A - C_A(\Delta t_{BA})$ where $\tilde{t_A}$ is a constructed timing measurement that exhibits a symmetric arrival time response function and shown in fig.~\ref{fig:slope_correction} c.~
+
+The data representation and calibration curve shown in fig.~\ref{fig:slope_correction} a may be constructed with $t_B$ on the y-axis as well.
+Then the PNR corrections are applied the the $t_B$ measurements instead.
+However, the resulting histograms $\tilde{t_B}$ are virtual identical to $\tilde{t_A}$.
 

### 2023-10-24 manuscript.tex
overleaf update

@@
 We label the measurements from the low (8~mV) and high (50~mV) trigger levels as $t_A$ and $t_B$ respectively.
-As shown in fig.~\ref{fig:waveform}, histograms of these arrival events are multimodal due to the PNR response.
+As shown in Fig.~\ref{fig:waveform}, histograms of these arrival events are multimodal due to the PNR response.
 We first present a method for recovering a symmetric arrival time response function using the the slope measurement $\Delta t_{BA} = t_B - t_A$.
@@
 \centering
-\includegraphics[width=0.75\textwidth]{./figs_03/slope_cancellation_light.pdf}
+\includegraphics[width=1\textwidth]{./figs_03/slope_cancellation_light.pdf}
 \caption[{PNR Slope Variation Analysis and Cancellation}]{\textbf{PNR Slope Variation Analysis and Cancellation} a) 2D histogram of RF pulse measurements.

### 2023-10-24 manuscript.tex
overleaf update

@@
 Photon number effects are especially evident in this lower jitter variety of SNSPD due to the use of impedance matching tapers which more efficiently couple energy out of the nanowire and into the readout circuit.
-With high resolution time tagging equipment, photon number dependent effects have even been observed in SNSPDs not necessarily designed to exhibit it \citep[\cite{sauer2023resolving}]{schapeler2023superconducting} like those without tapers \cite{Cahall2017SlewRatePNR}.
+With high resolution time tagging equipment, photon number dependent effects have even been observed in SNSPDs not necessarily designed to exhibit it \cite{schapeler2023superconducting, sauer2023resolving} like those without tapers \cite{Cahall2017SlewRatePNR}.
 Therefore it is increasingly likely that future research involving low-jitter SNSPDs and multiphoton pulsed sources will have to explicitly manage the PNR response for accurate time-correlated measurements -- whether the effect it is desired or not.

### 2023-10-26 manuscript.tex
overleaf update

@@
 \centering
-\includegraphics[width=1\textwidth]{./figs_03/fig_intro_2_light.pdf}
+\includegraphics[width=1\textwidth]{./figs/fig_intro_2_light.pdf}
 \caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) Diagram of the expiremental setup.
@@
 An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data.
-c) \textbf{\hl{XXXXXXXX}}}
+c) Scope trace of the RF pulse produced by the differential-readout tapered SNSPD.
+fig.~\ref{fig:waveform} zooms in on the rising edge outlined in red here}
 \label{fig:intro}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{./figs_03/waveform_light.pdf}
+\includegraphics[width=0.8\textwidth]{./figs/waveform_light.pdf}
 \caption[{PNR-sensitive Pulse Waveform}]{\textbf{PNR-sensitive Pulse Waveform} The rising edge of the differential SNSPD's RF pulses exhibit variations in height, slew rate, and arrival time due to photon-number dependent dynamics.
@@
 \centering
-\includegraphics[width=1\textwidth]{./figs_03/slope_cancellation_light.pdf}
+\includegraphics[width=1\textwidth]{./figs/slope_cancellation_light.pdf}
 \caption[{PNR Slope Variation Analysis and Cancellation}]{\textbf{PNR Slope Variation Analysis and Cancellation} a) 2D histogram of RF pulse measurements.

### 2023-11-08 manuscript.tex
overleaf update

@@
 
+We have shown that measurement of the slew rate or slope of SNSPD RF pulses may be useful for both photon number and arrival time discrimination.
+This is a fairly practical method that limited assumptions about the underlying modulation pattern of the optical signal.
+We show it allows for the measurement of pulse position modulation signals based on 10 and 20 Ghz clocks for which each optical pulse contains anywhere from 1 to 5 or more photons.
+
+We also present a 2-dimensional gaussian mixture model of the SNSPD response to the two trigger levels in an effort to model the available data as accurately and faithfully as possible.
+This may be used for photon number and arrival time discrimination as well.
+Assigning SNSPD detection events to photon number or PPM bins generalizes to assigning points in a 2-dimensional space to probability distributions built from gaussian mixtures.
+We show the gaussian mixture method moderately improves the accuracy of arrival time discrimination relative to the slope-based method.
+
+The full 2D treatment of photon number discrimination based on community detection of gaussian mixture groups is undeniably more complex than principle component analysis methods demonstrated in previous research\cite{sauer2023resolving, schapeler2023superconducting}.
+However, it's generality may be advantageous for future SNSPD systems that gather added data about the transient state of the SNSPD and readout circuitry.
+For example, more than two timing measurements from each SNSPD pulse may prove to be useful.
+Recent research has demonstrated that photon number information is present in the falling edge of the pulse \cite{sauer2023resolving, schapeler2023superconducting}, and, as shown here, timing measurements from two trigger levels on the rising edge are also useful.
+Therefore, the use of three or more unique time-correlated measurements may be advantageous.
+Digitizing the RF pulse with a high speed ADC or oscilloscope extends this thinking to many more measurements.
+Ultimately, photon number discrimination becomes a higher dimensional problem, for which gaussian mixture methods may outperform principle component analysis.
+
+Finally, higher dimensional analysis may be necessary when pulse overlap or time walk effects \cite{Mueller2023} complicate the nuanced photon number response characteristics of each SNSPD pulse.
+This is important in future SNSPD systems that are designed to exhibit both high maximum count rates \cite{Craiciu23} and photon number resolution.
+
+Bro. The 5 paragraph essay structure is literally just two stories slapped on top of each other. One with short contenxt, one with longer context.
+
 \bibliography{references}

### 2023-11-20 manuscript.tex
overleaf update

@@
 \begin{abstract*} 
-Superconducting Nanowire Single Photon Detectors are a type of time-correlated photon detector with low jitter performance especially in the mid-infrared.
+Superconducting Nanowire Single Photon Detectors have leading low-jitter performance, especially in the mid-infrared.
 They are useful for classical communication over high loss channels --such as across deep space-- and for quantum communication for which signals are restricted to the few-photon level.
@@
 Deep space optical communication has been a growing field of study in recent years, as space agencies look for ways to increase data rates to and from deep space missions.
-A key challenge in the development of this technology is closing the communication link over extremely large distances and high loss.
-This must be done given a restricted power budget available on the spacecraft, and therefore requires the use of photon efficient communication protocols that optimize the number of bits sent per unit of energy.
+A key challenge in this work is closing a communication link over extremely large distances and high loss.
+For data transmission from a power-limited spacecraft to earth, this must be done with a restricted power budge, and therefore requires the use of photon efficient communication protocols that optimize the number of bits sent per unit of energy.
 
 In this article, we demonstrate high rate Pulse Position Modulation (PPM) applicable to future deep space communication.
-This starts with a transmitter that sends an optical pulse in one of $2^M$ possible time slots measured with respect to a clock.
+A transmitter sends an optical pulse in one of $2^M$ possible time slots measured with respect to a clock.
 At a receiver, the arrival time of this pulse is measured to recover $M$ bits of encoded data.
@@
 
-The Deep Space Optical Communicaiton (DSOC) project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of 0.06 to 2.7 Au \cite{Srinivasan2023GroundReceiver}.
+The Deep Space Optical Communicaiton (DSOC) project managed by the Jet Propulsion Laboratory (JPL) demonstrates optical communication using PPM with the Psyche spacecraft from distances of 0.06 to 2.7 Au \cite{Srinivasan2023GroundReceiver}.
 
-For larger M, more data may be sent with a single optical pulse, thereby allowing a power limited spacecraft to send more data over a high loss optical channel back to earth.
-This is quantified through the photon information efficiency $c_p = C/E$ where $C$ is the link capacity and $E$ is the photon cost per optical pulse
+For larger M, more data may be sent with a single optical pulse or given spacecraft power budge.
+This is quantified through the photon information efficiency $c_p = C/E$ where $C$ is the link capacity and $E$ is the photon cost per optical pulse.
 
-The DSOC project uses M at least as high as 5, meaning 5 bits of data are send using 32 time slots per frame.
+The DSOC project uses PPM with maximum M values of at least 5, meaning 5 bits of data are sent using 32 time slots per frame.
 M values as high as 19 have been demonstrated in the lab~\cite{essiambre2023record}, but the number of time bins needed per frame scales exponentially with the number of bits transmitted per pulse.
@@
 
-We demonstrate a high clock rate PPM protocol in the lab based on modulating a mode-locked laser and receiving pulses with a low jitter superconducting nanowire single photon detector (SNSPD) (fig.~\ref{fig:intro} (a)).We focus on demonstrating moderately large PIE, while also increasing the clock rate of the sytem by an order of magnitude relative to the DSOC platform (2~GHz).
+We demonstrate a high clock rate PPM protocol in the lab based on modulating a mode-locked laser and receiving pulses with a low jitter superconducting nanowire single photon detector (SNSPD) (fig.~\ref{fig:intro} (a)).We focus on demonstrating moderately large PIE, while also increasing the clock rate of the sytem by an order of magnitude relative to the DSOC platform (from 2~GHz to 20~GHz).
 By operating at both higher clock rate and PIE than DSOC, this system exemplifies how future iterations of DSOC may send data more quickly but also over greater distances with the same power budget.
@@
 
-However, these detectors exhibit photon number number dependent responses that affect the time-correlated measurements needed for high-rate PPM.
+However, these detectors exhibit a photon number dependent response that affects the time-correlated measurements needed for high-rate PPM.
 This behavior, shown in Fig.~\ref{fig:waveform} is also known as photon number resolution (PNR) -- a property that is desirable in certain applications including quantum communication and quantum computing.
@@
 For the tapered differential detectors, the PNR response affects timing of fixed threshold timetaggs at any trigger level (fig.~\ref{fig:waveform}).
-However, at higher trigger levels the PNR response is less pronounced and the timing measurements are less affected.
-Therefore, we divide a single SNSPD readout line using an RF splitter and trigger on the RF pulse at a high and low level as shwon by the red lines in fig.~\ref{fig:waveform}.
-This allows us to extract the somewhat conjugate information of pulse arrival time and photon number.
+However, at lower trigger levels the PNR response is less pronounced and the timing measurements are less affected.
+Therefore, we divide a single SNSPD readout line using an RF splitter and trigger on the RF pulse at a high and low level as shown by the red lines in fig.~\ref{fig:waveform}.
+This gives partially conjugate information on optical pulse arrival time and photon number.
 From these measurements we study the PNR response in detail and present two methods for managing it.
@@
 The work here highlights the application of low jitter single-photon detectors for optical communication, which is impactful for deep-space optical communication as well as classical communication in quantum networks.
-Although single-photon counting is well estanblished for deep-space optical communication~\cite{Srinivasan2023GroundReceiver} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs.
-However, with the eachievement of high data rates recently achieved with photon-counting classical communication, these approaches can now be seriously considered for quantum networks.
-The main driver is the reduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
-\textbf{\hl{Calculate reduction in power from state of the art SFP modules}}
+Although single-photon counting is well estanblished for deep-space optical communication~\cite{Srinivasan2023GroundReceiver} so far it has not been utilized in quantum networks, which have so far relied on off-the-shelf SFP modules and DWDMs.
+However, when quantum channels are frequency multiplexed with much higher power classical channels, Raman scattered photons from the classical channel pollute the quantum channel~\cite{EraerdsRaman}.
+
+Attenuating classical communication to near the single photon level would solve this issue and require minimal added resources, as single photon detectors are already required at quantum nodes.
+DSOC demonstrates a promising approach to low-power classical communication based on phon counting and PPM which can be adapted for terrestrial quantum networks.
 
@@
 
-In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays.
+In the future, the performance of the optical communication system could be improved by using high count rate SNSPD arrays.
 Recently published high-count rate arrays have figures of merit of \textbf{\hl{$FoM_T$ for Peacoq and Resta2023 results}}.
@@
 
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
 We have shown that measurement of the slew rate or slope of SNSPD RF pulses may be useful for both photon number and arrival time discrimination.
@@
 
-Bro. The 5 paragraph essay structure is literally just two stories slapped on top of each other. One with short contenxt, one with longer context.
-
 \bibliography{references}
